Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-08-15 doc/report/msc-report.tex
cleaned 6.

Says Wikipedia: "Organizations generally start off with relatively simple use
of data warehousing. Over time, more sophisticated use of data warehousing
evolves." Zohmg is that relatively simple data warehouse; the seed from which
a more sophisticated data warehouse may evolve.

There is as of yet no support for specifying granularities. The only supported
resolution of time is the day.

The single aggregation performed is summing of the measurements. Future work
may include average, max and min, etc.

There is no metadata store. It would be very helpful for the application
writer to know what the known values are for each dimension.

It'd be interesting to think a bit about how the data store could be fully
elastic, i.e. not require any data set definition from the user and instead
create column-families on the fly based on the dimensions output from the
user's map.

\subsection*{Multiple Data Sets}

Proper support for multiple data sets in a Zohmg project.

\subsection*{Metadata}

data set introspection

roll-up and drill-down

good when creating apps

\subsection*{Updating Data Set Files}

Update tables on changes in configuration---data set files.

\subsection*{Importing Without MapReduce}

Importing content without firing of a MapReduce job, e.g. via a Thrift
service.

@@

Last.fm is investigating the possibility for using Zohmg for multiple
application areas, such as radio stats and web page stats.

>>>>

Says Wikipedia: "Organizations generally start off with relatively simple use of
data warehousing. Over time, more sophisticated use of data warehousing
evolves." Zohmg is a simple data warehouse; the seed from which a more
sophisticated data warehouse may evolve.

There is as of yet no support for specifying granularities. The only supported
resolution of time is the day. Future work could include adding support for
querying data at any level of granularity.

The single act of aggregation performed is the summing of the measurements.
Future work may include average, max and min, etcetera.

There is no metadata store. It would be very helpful for the application writer
to know what the known values are for each dimension. Future work could include
a metadata service with a simple Thrift interface at which the user can query
for dimensions, their respective cardinalities and values, etcetera.

@@

Last.fm will use for Zohmg in multiple instances of data analysis, most
prominently in the field of web log analysis.
